---
title: "Overall survival of patients with different BRCA1 status and BRCA1-like status: results from multiple imputation"
author: "Yuwei Wang"
date:  "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
  toc_depth: 3  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Read me
This script codes the results from the study entitled Long-term outcomes of young, node-negative, chemotherapy-naive, triple-negative breast cancer patients according to BRCA1 status. The script generated results of overall survival and overall survival with additional adjustment for second primary tumors in
**Table 2. (Subdistribution) hazard ratios for 15-year overall survival, distant recurrence-free survival, and second primary tumors according to BRCA1 status, based on multiple-imputed data**, **Supplementary Table S6. Hazard ratios for overall survival according to BRCA1 status, based on multiple-imputed data**, and **Supplementary Table S10. Univariable (subdistribution) hazard ratios according to BRCA1-like status**.


## Load the libraries and functions
```{r load.libraries and functions, message=F, warning=F}
library('readxl')
library('rms')
library('ggplot2')
library('plyr')
library('dplyr')
library('xtable')
library('tidyr')
library("stringr")
library('lubridate')
library('riverplot')
library("knitr")
library("survminer")
library('survival')
library("xfun")
library("table1")
library("cmprsk")
library("mice")
library("tidyverse")
library("mstate")
library("VIM")
library("mstate")

res_table<-function(X){
  sumX<-summary(pool(X), conf.int = TRUE) #summary the pooled model results
  res<-c()
  row<-nrow(sumX)
  for (i in c(1:row)){ #make the (exp) results into a matrix format(round(a), nsmall = 2)
    res0 <- c(format(round(exp(sumX[i,2]), 2), nsmall = 2), 
            format(round(exp(sumX[i,7]), 2), nsmall = 2),
            format(round(exp(sumX[i,8]), 2), nsmall = 2))
    res <- append(res, res0)}
    HRs <- matrix(res, nrow=row, byrow=T)
    groupHRs <- paste0(HRs[,1], " (", HRs[,2], "-", HRs[,3],")")
  cbind(as.character(sumX[, 1]), groupHRs) #bind the row names (variable names) to the corresponding results
  
}
```
res_table is a function to extract hazard ratios and confidence intervals from the summary of the pooled results of the survival analysis.

## Multiple imputation
```{r load.data, include=FALSE}
TNBC<-read.csv("/DATA/users/yu.wang/7_BRCAness/long-term survival according to BRCA1 status/dataset/TNBC485_BRCA1statusupdate_in_August_2022.csv")
TNBC$X<-NULL
```

```{r prepare pre imputation data, include=FALSE}
TNBC$BRCA2[which(TNBC$BRCA2 == "tBRCA2m")] <- NA

TNBC$H.tilde.os <- nelsonaalen(TNBC, time15, death15)
summary(TNBC$H.tilde.os)
##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
##  0.0000  0.2794  0.3364  0.2847  0.3364  0.3364

table(TNBC$push.bordercat4)
## 
##   0   1   2   3 
## 186  56  78 152

TNBC$push.bordercat4<-factor(TNBC$push.bordercat4)
table(TNBC$FIBROTIC_FOCUS_REVISION_E1_C1)
## 
##   0   1   2   3   4   5   6   7   8   9  10  11  12  13  15  16  17 
## 346  10  19  21  16  17  11  12  10   4   7   3   3   2   1   1   2

tobeimpu<-c("palga_nr","incyear","T_LEEFT",
           "tumorsize","tumorsize.cat","Grade","HISTOLOGICAL_SUBTYPErec","ER.num", "PR.num",
           "push.bordercat4","lym.vas.inv", "sTILs","FIBROTIC_FOCUS_REVISION_E1_C1","centr_necrosis_cat",
           "BRCA1like","gBRCA1","sBRCA1","BRCA2","BPM",
           "Surgery","Radiotherapy", "H.tilde.os","death15","time15")
data<-TNBC[, tobeimpu]
aggr(data, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, 
     labels=names(data), cex.axis=.7, gap=3, 
     ylab=c("Histogram of missing data","Pattern"))

data$gBRCA1 <- as.factor(data$gBRCA1)
data$sBRCA1 <- as.factor(data$sBRCA1)
data$BPM <- as.factor(data$BPM)
data$BRCA1like <- as.factor(data$BRCA1like)
data$BRCA2 <- as.factor(data$BRCA2)
data$Radiotherapy <- as.factor(data$Radiotherapy)
data$lym.vas.inv <- as.factor(data$lym.vas.inv)
table(TNBC$tumorsize.cat[which(is.na(TNBC$tumorsize))])#we can do a conditional imputation

## 
##  1 1B 1C  2 
##  4  4 22 21

data$tumorsize.cat <- as.numeric(as.factor(data$tumorsize.cat))
data$tumorsize.cat[which(is.na(data$tumorsize.cat))]<-999
table(data$tumorsize.cat)

## 
##   1   2   3   4   5   6 999 
##   4   3  40 238 188  10   2

#1->1(1mm-20mm); 2->1a(1-5mm); 3->1B(6-10mm); 4->1C(11-20mm); 5->2(21-50mm); 6->3(>50mm); 999->NA

#before we impute the BRCA1 status, we first solve the missingness by the mutual exclusive assumption
data$BPM[which(data$gBRCA1==1 | data$sBRCA1==1)]<-0
data$gBRCA1[which(data$BPM==1)]<-0
data$sBRCA1[which(data$BPM==1)]<-0
```


```{r multiple-imputation, echo=T, results='hide'}
ini <- mice(data, maxit=0, vis="monotone",print=FALSE) 

## Warning: Number of logged events: 4

meth <- ini$meth
meth

meth["push.bordercat4"]<-"polr"

pred<-quickpred(data, exclude=c("palga_nr","time15", "drfs15","time15.drfs","idfs15","time15.idfs", 
                                "tumorsize.cat", "ER.num", "PR.num"), 
                include = c("tumorsize","Grade","HISTOLOGICAL_SUBTYPErec","push.bordercat4","lym.vas.inv",
                            "sTILs","FIBROTIC_FOCUS_REVISION_E1_C1","centr_necrosis_cat",
                            "gBRCA1","sBRCA1","BRCA2","BPM", "BRCA1like",
                            "Surgery","Radiotherapy","H.tilde.os", "death15"), 
                minpuc = 0.2, mincor = 0.1) 
#pred#column shows if this variable predict the value of the row variable
pred[c("tumorsize.cat"),] # all 0

post<-ini$post
post["tumorsize"] <-"imp[[j]][data$tumorsize.cat[!r[,j]]==1, i] <- squeeze(imp[[j]][data$tumorsize.cat[!r[,j]]==1, i], c(1, 20));imp[[j]][data$tumorsize.cat[!r[,j]]==2, i] <- squeeze(imp[[j]][data$tumorsize.cat[!r[,j]]==2, i], c(1, 5)); imp[[j]][data$tumorsize.cat[!r[,j]]==3, i] <- squeeze(imp[[j]][data$tumorsize.cat[!r[,j]]==3, i], c(6, 10));imp[[j]][data$tumorsize.cat[!r[,j]]==4, i] <- squeeze(imp[[j]][data$tumorsize.cat[!r[,j]]==4, i], c(11, 20));imp[[j]][data$tumorsize.cat[!r[,j]]==5, i] <- squeeze(imp[[j]][data$tumorsize.cat[!r[,j]]==5, i], c(21, 50)); imp[[j]][data$tumorsize.cat[!r[,j]]==6, i] <- squeeze(imp[[j]][data$tumorsize.cat[!r[,j]]==6, i], c(51, 150))"

post["BPM"]<-"imp[[j]][data$gBRCA1[!r[,j]]==1, i] <- 0; imp[[j]][data$sBRCA1[!r[,j]]==1, i] <- 0"

## Impute
seed <- 11200 # to reproduce results

impute <- mice(data=data, m=20, seed=seed, meth=meth, pred=pred, maxit=25, post = post, vis="monotone")
```

```{r impuation plot}
plot(impute, c("BRCA1like","gBRCA1","sBRCA1","BPM","sTILs","tumorsize","push.bordercat4"))
```

### Redefine variables for analysis after multiple imputation
```{r redefining variables after multiple imputation}
impTNBC <- mice::complete(impute, "long", FALSE) %>%
  mutate(tumorsize.cat2 = ifelse(tumorsize <= 20, "1", "2-3"),
         Grade.cat2 = ifelse(Grade == "Grade 3", 1, 0),
         hist_subtype.cat3 = ifelse(HISTOLOGICAL_SUBTYPErec=="Carcinoma NST" | HISTOLOGICAL_SUBTYPErec=="Metaplastic carcinoma", 
                                   HISTOLOGICAL_SUBTYPErec, "Other"),
         treatment.cat3 = ifelse(str_detect(Surgery,"lumpectomy") & Radiotherapy==1, "lumpectomy + RT",
                               ifelse(str_detect(Surgery,"mastectomy") & Radiotherapy==0, "mastectomy","Other")),
         sBRCA1 = if_else(gBRCA1 == 0 & sBRCA1 == 1, 1, 0), #use if_else to avoid the problem when converting factors
         BRCA1BPM = ifelse(BPM == 1, "BPM",
                           ifelse(gBRCA1 == 1, "gBRCA1m",
                                  ifelse(sBRCA1 == 1, "sBRCA1m",
                                         ifelse(BPM == 0 & gBRCA1 == 0 & sBRCA1 == 0, "BRCA1 non-altered", NA))))) %>%
  mutate(BRCA1BPM = relevel(factor(BRCA1BPM), ref = ("BRCA1 non-altered")),
         dum.nonaltered = ifelse(BRCA1BPM == "BRCA1 non-altered", 1, 0))

```

```{r number of patients, include=FALSE}
#check number of patients for the analysis
totalnum <- filter(impTNBC, impTNBC$BRCA2 != "gBRCA2m")
median(c(table(totalnum$.imp)))#478.5
median(c(table(totalnum$.imp, totalnum$incyear <= 1997)[, 2])) #421.5
median(c(table(totalnum$.imp, totalnum$ER.num == 0)[, 2])) #454.5
median(c(table(totalnum$.imp, totalnum$BRCA1like == 1)[, 2]))#401
```
For the survival analysis, we excluded women with a germline BRCA2 mutation.
```{r imputation list}
implist<-list()
for(i in (1:20)){
  list0<-filter(impTNBC, impTNBC$.imp==i & impTNBC$BRCA2 != "gBRCA2m")
  implist<-append(implist, list(list0))
}
```


## Overall survival according to BRCA1 status and BRCA1-like status
### According to BRCA1 statuses 
The codes below return the results from Table 2 (overall survival and overall survival with additional adjustment for second primary tumors), and Supplementary Table S6 (All patients, and all patients (additional adjustment for second primary tumors)).

Results from univariable analysis with only BRCA1 status.
```{r OS BRCA1 status uni}
#check proportional hazard
coxzph.uni.BRCA1BPM.all<- as.mira(lapply(implist, function(x){
                              cox.zph(coxph(Surv(time15, death15) ~ BRCA1BPM, data=x), terms = F)
                              }))#good
coxzph.uni.BRCA1BPM.all$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.all$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.all$analyses[[sample(1:20, 1)]]
#gBRCA1m not PH


#split the dataset at about 3 years after survival. This decison was made according to the Schoenfield residual plots in the complete case analysis.
impTNBC.os.episode <- survSplit(Surv(time15, death15)~. , data = filter(impTNBC, impTNBC$BRCA2 != "gBRCA2m"),
                                cut = c(3), id = "id", episode = "episode")

implist.os.episode <- list()
for(i in (1:20)) { 
  implist.os0 <- filter(impTNBC.os.episode, impTNBC.os.episode$.imp == i)
  implist.os.episode <- append(implist.os.episode, list(implist.os0))
}

#BRCA1 status was included as three dummy variables:
coxzph.uni.BRCA1BPM.all.tv <- as.mira(lapply(implist.os.episode, function(x){
                              cox.zph(coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1==0) + sBRCA1 + BPM, data=x))
                              }))#good
coxzph.uni.BRCA1BPM.all.tv $analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.all.tv $analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.all.tv $analyses[[sample(1:20, 1)]]

uni.BRCA1BPM.all <- as.mira(lapply(implist.os.episode, function(x){
                   coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1==0) + sBRCA1 + BPM, data=x)
                  }))

summary(pool(uni.BRCA1BPM.all))
res_table(uni.BRCA1BPM.all)
```
Results from multivariable analysis with BRCA1 status, sTILs, and other covariates.
```{r OS BRCA1 status multi}
#First check if there are interaction effect between BRCA1 status and sTILs
multi.BRCA1BPM.check <- as.mira(lapply(implist.os.episode, function(x){
                      coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + 
                      sTILs + tumorsize.cat2 + Grade.cat2 + hist_subtype.cat3 + lym.vas.inv + 
                        treatment.cat3 + gBRCA1:sTILs + sBRCA1:sTILs + BPM:sTILs, data=x) }))
res_table(multi.BRCA1BPM.check)

#Only the interaction between BRCA1-PM and sTILs was statistically significant. Therefore, only that term was kept in the final model.
multi.BRCA1BPM.all <- as.mira(lapply(implist.os.episode, function(x){
                   coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + 
                      sTILs + tumorsize.cat2 + Grade.cat2 + hist_subtype.cat3 + lym.vas.inv + 
                        treatment.cat3 + BPM:sTILs, data=x)
                  }))

summary(pool(multi.BRCA1BPM.all))#P interaction = 0.03
res_table(multi.BRCA1BPM.all)
```

Add second primary tumor as a time-varying covariate to check the effect of second primary tumor on overall survival.
```{r add second primary tumor}
TNBC_SPT <- survSplit(Surv(time, death)~. , data= TNBC,
                                  cut=c(15), id="id", episode = "episode") %>%
  filter(episode == 1) %>%
  #select(-id, -episode) %>%
  mutate(first.tumor.incdat = as.Date(first.tumor.incdat, format = "%Y-%m-%d"),
         SPT.inc15 = first.tumor.incdat,
         incdat = as.Date(incdat, format = "%Y-%m-%d"),
         VITDAT.final = as.Date(VITDAT.final, format="%Y-%m-%d")) %>%
  mutate(SPT.inc15 = ifelse((first.tumor.incdat - incdat)/365.25 <= 15, SPT.inc15, NA)) %>%
  mutate(SPT.inc15 = as.Date(SPT.inc15, origin = "1970-01-01"))

TNBC_SPT$id <- NULL
TNBC_SPT$episode <- NULL
secondprim <- with(TNBC_SPT, data.frame(palga_nr = palga_nr,
                                    time=time,
                                    second.prim.time= ifelse(SPT.inc15== VITDAT.final,
                                                             (SPT.inc15 - incdat)/365.25 - 0.1,
                                                             (SPT.inc15 - incdat)/365.25),
                                    death = death))

TNBC_SPT <- tmerge(TNBC_SPT, secondprim, id=palga_nr,
                 death = event(time, death),
                 secondtumor = tdc(second.prim.time),
                 options= list(idname="palga_nr"))
#split the dataset at 3 years after survival because the hazard of germline BRCA1 mutation as not proportional.
TNBC_SPT_cutoff3 <- survSplit(Surv(tstart, tstop, death)~. , data= TNBC_SPT,
                 cut=c(3), id="id", episode = "episode")
```

```{r add SPT sanity check, include=FALSE}
TNBC_SPT[c(1:20), c("palga_nr", "tstart", "tstop","secondtumor")]
TNBC_SPT_cutoff3[c(1:20), c("palga_nr", "tstart", "tstop","secondtumor","episode", "death")]
```

```{r adding SPT_prepare the dataset}
impvar <- c(".imp","palga_nr", "incyear","gBRCA1", "sBRCA1", "BPM","BRCA2","sTILs",  "tumorsize.cat2", 
            "ER.num", "PR.num", "BRCA1like", "Grade.cat2","hist_subtype.cat3", "lym.vas.inv",  "treatment.cat3")
sptvar <- c("palga_nr", "tstart", "tstop","secondtumor","episode", "death")
impTNBC_SPT_os <- merge(impTNBC[, c(impvar)],  TNBC_SPT_cutoff3[, c(sptvar)], 
              by.x = "palga_nr", by.y = "palga_nr", all.x = T, all.y = T)
names(impTNBC_SPT_os)          

implist_secondprim <- list()
for(i in (1:20)){
  list0 <- filter(impTNBC_SPT_os, impTNBC_SPT_os$.imp == i & impTNBC_SPT_os$BRCA2 != "gBRCA2m")
  implist_secondprim <- append(implist_secondprim, list(list0))
}
```

```{r final SPT dataset sanity check, include=FALSE}
head(implist_secondprim[[1]][, c("palga_nr", "tstart", "tstop", "secondtumor", "death")], 20)
#note that death reflects the death status within 15 years FUP
```

```{r mutivariable wiht SPT}
multi.BRCA1BPM.STP.all <- as.mira(lapply(implist_secondprim, function(x){
                        coxph(Surv(tstart, tstop, death) ~ strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + sTILs + BPM:sTILs
                              + tumorsize.cat2 + Grade.cat2 + hist_subtype.cat3 + lym.vas.inv + treatment.cat3 + secondtumor, 
                              data=x)}))
summary(pool(multi.BRCA1BPM.STP.all))
res_table(multi.BRCA1BPM.STP.all)
```


```{r stratify analysis, include=F}
implist.BPM <- list()
for(i in (1:20)){
  list0 <- filter(impTNBC, impTNBC$.imp==i & impTNBC$BRCA2 != "gBRCA2m" & impTNBC$BPM == 1)
  
  implist.BPM <- append(implist.BPM, list(list0))
}

implist.gBRCA1 <- list()
for(i in (1:20)){
  list0 <- filter(impTNBC, impTNBC$.imp==i & impTNBC$BRCA2 != "gBRCA2m" & impTNBC$gBRCA1 == 1)
  
  implist.gBRCA1 <- append(implist.gBRCA1, list(list0))
}

implist.nonaltered <- list()
for(i in (1:20)){
  list0 <- filter(impTNBC, impTNBC$.imp==i & impTNBC$BRCA2 != "gBRCA2m" & impTNBC$BRCA1BPM == "BRCA1 non-altered")
  
  implist.nonaltered <- append(implist.nonaltered, list(list0))
}

#all patients with interaction terms, remove hist_subtypes, otherwise one of the subgroup analysis wont converge
mod.strata.all <- as.mira(lapply(implist.os.episode, function(x){
                   coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + 
                      sTILs + tumorsize.cat2 + Grade.cat2 + lym.vas.inv + 
                        treatment.cat3 + BPM:sTILs, data=x)
                  }))
res_table(mod.strata.all) 
#                                                   groupHRs          
#  [1,] "sBRCA1"                                    "1.03 (0.45-2.35)"
#  [2,] "BPM1"                                      "1.15 (0.64-2.06)"
#  [3,] "sTILs"                                     "0.84 (0.78-0.91)"
#  [4,] "tumorsize.cat22-3"                         "1.47 (1.03-2.11)"
#  [5,] "Grade.cat2"                                "1.47 (0.89-2.43)"
#  [6,] "lym.vas.inv1"                              "2.50 (1.62-3.86)"
#  [7,] "treatment.cat3mastectomy"                  "1.34 (0.91-1.97)"
#  [8,] "treatment.cat3Other"                       "1.51 (0.82-2.80)"
#  [9,] "strata(episode)episode=1:gBRCA1 == 0FALSE" "0.76 (0.37-1.56)"
# [10,] "strata(episode)episode=2:gBRCA1 == 0FALSE" "2.17 (1.22-3.85)"
# [11,] "strata(episode)episode=1:gBRCA1 == 0TRUE"  "NA (NA-NA)"      
# [12,] "strata(episode)episode=2:gBRCA1 == 0TRUE"  "NA (NA-NA)"      
# [13,] "BPM1:sTILs"                                "0.82 (0.69-0.99)"


mod.strata.BPM <- as.mira(lapply(implist.BPM, function(x){
                   coxph(Surv(time15, death15) ~ sTILs + tumorsize.cat2 + Grade.cat2 + lym.vas.inv + 
                        treatment.cat3, data=x)
                  }))
res_table(mod.strata.BPM)
#                                 groupHRs          
# [1,] "sTILs"                    "0.70 (0.59-0.83)"
# [2,] "tumorsize.cat22-3"        "1.61 (0.74-3.50)"
# [3,] "Grade.cat2"               "1.23 (0.41-3.67)"
# [4,] "lym.vas.inv1"             "1.55 (0.53-4.55)"
# [5,] "treatment.cat3mastectomy" "0.98 (0.39-2.51)"
# [6,] "treatment.cat3Other"      "0.95 (0.20-4.43)"

mod.strata.gBRCA1 <- as.mira(lapply(implist.gBRCA1, function(x){
                   coxph(Surv(time15, death15) ~ sTILs + tumorsize.cat2 + Grade.cat2 + lym.vas.inv + 
                        treatment.cat3, data=x)
                  }))
res_table(mod.strata.gBRCA1)
#                                 groupHRs          
# [1,] "sTILs"                    "0.85 (0.76-0.94)"
# [2,] "tumorsize.cat22-3"        "1.43 (0.70-2.92)"
# [3,] "Grade.cat2"               "1.23 (0.49-3.11)"
# [4,] "lym.vas.inv1"             "3.54 (1.47-8.50)"
# [5,] "treatment.cat3mastectomy" "0.96 (0.47-1.96)"
# [6,] "treatment.cat3Other"      "1.08 (0.34-3.46)"

mod.strata.nonaltered <- as.mira(lapply(implist.nonaltered, function(x){
                   coxph(Surv(time15, death15) ~ sTILs + tumorsize.cat2 + Grade.cat2 + lym.vas.inv + 
                        treatment.cat3, data=x)
                  }))
res_table(mod.strata.nonaltered)
#                                 groupHRs          
# [1,] "sTILs"                    "0.83 (0.74-0.94)"
# [2,] "tumorsize.cat22-3"        "1.64 (0.85-3.19)"
# [3,] "Grade.cat2"               "2.07 (0.76-5.65)"
# [4,] "lym.vas.inv1"             "3.21 (1.35-7.62)"
# [5,] "treatment.cat3mastectomy" "2.11 (0.94-4.74)"
# [6,] "treatment.cat3Other"      "2.93 (0.92-9.32)"
```


### Accroding to BRCA1-like statuses 
The codes return the results for Supplementary Table S10.
Results from univariable analysis only including BRCA1-like status.
```{r OS BRCA1like status uni}
coxzph.uni.BRCA1like.all<- as.mira(lapply(implist, function(x){
                              cox.zph(coxph(Surv(time15, death15) ~ BRCA1like, data=x))
                              }))#good
coxzph.uni.BRCA1like.all$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1like.all$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1like.all$analyses[[sample(1:20, 1)]]

uni.BRCA1like <- as.mira(lapply(implist, function(x){
                   coxph(Surv(time15, death15) ~ BRCA1like, data=x)
                  }))
summary(pool(uni.BRCA1like))
res_table(uni.BRCA1like)
```

## Sensitivity analysis when inlcuding women diagnosed before 1997
The codes below return the results of Supplementary Table S6 (Patients diagnosed from 1989 - 1997).
```{r OS BRCA1 status_1989-1997}
implist.1997<-list()
for(i in (1:20)){
  list0<-filter(impTNBC, impTNBC$.imp==i & impTNBC$BRCA2 != "gBRCA2m" & impTNBC$incyear <= 1997)
  
  implist.1997 <- append(implist.1997, list(list0))
}
####univariable
coxzph.uni.BRCA1BPM.1997<- as.mira(lapply(implist.1997, function(x){
                              cox.zph(coxph(Surv(time15, death15) ~ gBRCA1 + sBRCA1 + BPM, data=x))
                              }))#good
coxzph.uni.BRCA1BPM.1997$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.1997$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.1997$analyses[[sample(1:20, 1)]]
#gBRCA1m not PH

impTNBC.os.episode.1997 <- survSplit(Surv(time15, death15)~. , data = filter(impTNBC, impTNBC$BRCA2 != "gBRCA2m" & impTNBC$incyear <= 1997),
                                cut = c(3), id = "id", episode = "episode")

implist.os.episode.1997  <- list()
for(i in (1:20)) { 
  implist.os0 <- filter(impTNBC.os.episode.1997, impTNBC.os.episode.1997$.imp == i)
  implist.os.episode.1997  <- append(implist.os.episode.1997 , list(implist.os0))
}


coxzph.uni.BRCA1BPM.1997.tv <- as.mira(lapply(implist.os.episode.1997, function(x){
                              cox.zph(coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1==0) + sBRCA1 + BPM, data=x))
                              }))#good
coxzph.uni.BRCA1BPM.1997.tv$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.1997.tv$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.1997.tv$analyses[[sample(1:20, 1)]]
#now looks good
uni.BRCA1BPM.1997 <- as.mira(lapply(implist.os.episode.1997, function(x){
                   coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1==0) + sBRCA1 + BPM, data=x)
                  }))
summary(pool(uni.BRCA1BPM.1997))
res_table(uni.BRCA1BPM.1997)

####multivariable
coxzph.BRCA1BPM.1997.tv <- as.mira(lapply(implist.os.episode.1997, function(x){
                         cox.zph(coxph(Surv(tstart, time15, death15) ~  strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + sTILs + 
                           BPM:sTILs + tumorsize.cat2 + Grade.cat2 + hist_subtype.cat3 + lym.vas.inv + treatment.cat3, data=x))
                         }))
coxzph.BRCA1BPM.1997.tv$analyses[[sample(1:20, 1)]]
coxzph.BRCA1BPM.1997.tv$analyses[[sample(1:20, 1)]]
coxzph.BRCA1BPM.1997.tv$analyses[[sample(1:20, 1)]]

multi.BRCA1BPM.1997 <- as.mira(lapply(implist.os.episode.1997, function(x){
                      coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + sTILs + 
                              BPM:sTILs + tumorsize.cat2 + Grade.cat2 +  hist_subtype.cat3 + lym.vas.inv + treatment.cat3, data=x)
                      }))
summary(pool(multi.BRCA1BPM.1997))
res_table(multi.BRCA1BPM.1997)
```
## Sensitivity analysis when including women with BRCA1like tumor
The codes below return the results of Supplementary Table S6 (Patients with BRCA1-like tumors).
```{r OS BRCA1 status_BRCA1like}
implist.BRCA1like<-list()
for(i in (1:20)){
  list0<-filter(impTNBC, impTNBC$.imp==i & impTNBC$BRCA2 != "gBRCA2m" & impTNBC$BRCA1like == 1)
  
  implist.BRCA1like <- append(implist.BRCA1like, list(list0))
}
####univariable
coxzph.uni.BRCA1BPM.BRCA1like<- as.mira(lapply(implist.BRCA1like, function(x){
                              cox.zph(coxph(Surv(time15, death15) ~ gBRCA1 + sBRCA1 + BPM, data=x))
                              }))#good
coxzph.uni.BRCA1BPM.BRCA1like$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.BRCA1like$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.BRCA1like$analyses[[sample(1:20, 1)]]
#I will still split the FUP time so it is easy to compare
impTNBC.os.episode.BRCA1like <- survSplit(Surv(time15, death15)~. , 
                                          data = filter(impTNBC, impTNBC$BRCA2 != "gBRCA2m" & impTNBC$BRCA1like == 1),
                                cut = c(3), id = "id", episode = "episode")

implist.os.episode.BRCA1like  <- list()
for(i in (1:20)) { 
  implist.os0 <- filter(impTNBC.os.episode.BRCA1like, impTNBC.os.episode.BRCA1like$.imp == i)
  implist.os.episode.BRCA1like  <- append(implist.os.episode.BRCA1like , list(implist.os0))
}

uni.BRCA1BPM.BRCA1like <- as.mira(lapply(implist.os.episode.BRCA1like, function(x){
                   coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1==0) + sBRCA1 + BPM, data=x)
                  }))
summary(pool(uni.BRCA1BPM.BRCA1like))
res_table(uni.BRCA1BPM.BRCA1like)

#multivariable
coxzph.BRCA1BPM.BRCA1like.tv <- as.mira(lapply(implist.os.episode.BRCA1like, function(x){
                         cox.zph(coxph(Surv(tstart, time15, death15) ~  strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + sTILs + 
                         BPM:sTILs + tumorsize.cat2 + Grade.cat2 + hist_subtype.cat3 + lym.vas.inv + treatment.cat3, data=x))
                         }))
coxzph.BRCA1BPM.BRCA1like.tv$analyses[[sample(1:20, 1)]]
coxzph.BRCA1BPM.BRCA1like.tv$analyses[[sample(1:20, 1)]]
coxzph.BRCA1BPM.BRCA1like.tv$analyses[[sample(1:20, 1)]]

multi.BRCA1BPM.BRCA1like <- as.mira(lapply(implist.os.episode.BRCA1like, function(x){
                      coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + sTILs + 
                      BPM:sTILs + tumorsize.cat2 + Grade.cat2 +  hist_subtype.cat3 + lym.vas.inv + treatment.cat3, data=x)
                      }))
summary(pool(multi.BRCA1BPM.BRCA1like))
res_table(multi.BRCA1BPM.BRCA1like)
```

## Sensitivity analysis when including women with ER and PR expression in the tumor < 1%
The codes below return the results of Supplementary Table S6 (Patients with ER and PR expression in the tumor < 1%).
```{r OS BRCA1 status_1%cutoff}
implist.cutoff<-list()
for(i in (1:20)){
  list0<-filter(impTNBC, impTNBC$.imp==i & impTNBC$BRCA2 != "gBRCA2m" & impTNBC$ER.num == 0 & impTNBC$PR.num == 0)
  
  implist.cutoff <- append(implist.cutoff, list(list0))
}
####univariable
coxzph.uni.BRCA1BPM.cutoff<- as.mira(lapply(implist.cutoff, function(x){
                              cox.zph(coxph(Surv(time15, death15) ~ gBRCA1 + sBRCA1 + BPM, data=x))
                              }))#good
coxzph.uni.BRCA1BPM.cutoff$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.cutoff$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.cutoff$analyses[[sample(1:20, 1)]]
#gBRCA1m not PH

impTNBC.os.episode.cutoff <- survSplit(Surv(time15, death15)~. , 
                             data = filter(impTNBC, impTNBC$BRCA2 != "gBRCA2m" & impTNBC$ER.num == 0 & impTNBC$PR.num == 0),
                             cut = c(3), id = "id", episode = "episode")

implist.os.episode.cutoff  <- list()
for(i in (1:20)) { 
  implist.os0 <- filter(impTNBC.os.episode.cutoff, impTNBC.os.episode.cutoff$.imp == i)
  implist.os.episode.cutoff  <- append(implist.os.episode.cutoff , list(implist.os0))
}


coxzph.uni.BRCA1BPM.cutoff.tv <- as.mira(lapply(implist.os.episode.cutoff, function(x){
                              cox.zph(coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1==0) + sBRCA1 + BPM, data=x))
                              }))#good
coxzph.uni.BRCA1BPM.cutoff.tv$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.cutoff.tv$analyses[[sample(1:20, 1)]]
coxzph.uni.BRCA1BPM.cutoff.tv$analyses[[sample(1:20, 1)]]
#now looks good
uni.BRCA1BPM.cutoff <- as.mira(lapply(implist.os.episode.cutoff, function(x){
                   coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1==0) + sBRCA1 + BPM, data=x)
                  }))
summary(pool(uni.BRCA1BPM.cutoff))
res_table(uni.BRCA1BPM.cutoff)

####multivariable
coxzph.BRCA1BPM.cutoff.tv <- as.mira(lapply(implist.os.episode.cutoff, function(x){
                         cox.zph(coxph(Surv(tstart, time15, death15) ~  strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + sTILs + 
                         BPM:sTILs + tumorsize.cat2 + Grade.cat2 + hist_subtype.cat3 + lym.vas.inv + treatment.cat3, data=x))
                         }))
coxzph.BRCA1BPM.cutoff.tv$analyses[[sample(1:20, 1)]]
coxzph.BRCA1BPM.cutoff.tv$analyses[[sample(1:20, 1)]]
coxzph.BRCA1BPM.cutoff.tv$analyses[[sample(1:20, 1)]]

multi.BRCA1BPM.cutoff <- as.mira(lapply(implist.os.episode.cutoff, function(x){
                      coxph(Surv(tstart, time15, death15) ~ strata(episode):(gBRCA1 == 0) + sBRCA1 + BPM + sTILs + 
                              BPM:sTILs + tumorsize.cat2 + Grade.cat2 +  hist_subtype.cat3 + lym.vas.inv + treatment.cat3, data=x)
                      }))
summary(pool(multi.BRCA1BPM.cutoff))
res_table(multi.BRCA1BPM.cutoff)
```

```{r summary results, include=FALSE}
res.sum <- cbind(rbind(res_table(uni.BRCA1BPM.all), res_table(multi.BRCA1BPM.all)),
                  rbind(res_table(uni.BRCA1BPM.1997),  res_table(multi.BRCA1BPM.1997)),
                  rbind(res_table(uni.BRCA1BPM.cutoff),  res_table(multi.BRCA1BPM.cutoff)),
                  rbind(res_table(uni.BRCA1BPM.BRCA1like),  res_table(multi.BRCA1BPM.BRCA1like))) %>%
  as_tibble() %>%
  .[, c(1, 2, 4, 6, 8)] %>%
      rename(Var = V1,
         HR = groupHRs) %>%
  filter(!str_detect(HR, "NA")) %>%
  mutate(Var = ifelse(str_detect(Var, "episode=1"), "gBRCA1 0-3years",
                      ifelse(str_detect(Var, "episode=2"), "gBRCA1 4-15years",Var))) %>%
  .[c(3, 4, 1, 2, 15, 16, 5:7, 17, 8:14),]

res.sum

res.all.SPT <- res_table(multi.BRCA1BPM.STP.all) %>%
  as_tibble() %>%
    rename(Var = V1,
         HR = groupHRs) %>%
  filter(!str_detect(HR, "NA")) %>%
  mutate(Var = ifelse(str_detect(Var, "episode=1"), "gBRCA1 0-3years",
                      ifelse(str_detect(Var, "episode=2"), "gBRCA1 4-15years",Var))) %>%
  .[c(12, 13, 1:3, 14, 4:11),] 
res.all.SPT
```

## Session information
```{r sinfo}
sessionInfo()
```